Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
nested pipelines example (maybe subsection?)

>>>>

% XXX do we need a subsection header here?
% "Recursive composition of estimators"?
Figure~\ref{nested-gridsearch} shows how different meta-estimators interact.
This snippet builds a composite estimator in several steps.
First, a linear SVM classifier is combined in a pipeline with
a feature selector based on $\chi^2$ test statistics.
This is then fed as input to a \texttt{OneVsRestClassifier}
to build a $K$-way multiclass estimator
consisting of $K$ binary classifiers,
after determining the value of $K$ at \texttt{fit} time
from the training labels.
Each of these binary classifiers performs feature selection
independently of all the others.
This composite classifier is then combined
with a \textsf{tf--idf} feature extractor using yet another pipeline.
Because the result is again an estimator,
we can perform grid search to find optimal values for the hyper-parameters
of each step of the recursive pipeline.

The \texttt{param\_grid} in Figure~\ref{nested-gridsearch}
uses a \sklearn-specific notation
to address the individual components of the nested structure.
This notation uses double underscores to separate components,
so that \texttt{tfidf\_\_sublinear\_tf}
addresses the \texttt{sublinear\_tf} setting
of the \textsf{tf--idf} feature extractor
(when turned on, term frequencies are replaced by their logarithms).
Note the \texttt{estimator} component,
which address the base estimator (the first pipeline)
inside the OvR meta-estimator.
This is required because the wrapper may itself have settings
that might conflict with the estimator that it wraps;
this is not required for pipelines,
because those have no settings of their own.

\begin{figure}[t]
\begin{pythoncode}
from sklearn.grid_search import GridSearchCV
from sklearn.feature_extraction.text import TfidfVectorizer
from sklearn.feature_selection import SelectKBest, chi2
from sklearn.multiclass import OneVsRestClassifier
from sklearn.pipeline import Pipeline
from sklearn.svm import LinearSVC

svm_chi2 = Pipeline([("chi2", SelectKBest(chi2)),
                     ("svm", LinearSVC())])
ovr_svm = OneVsRestClassifier(svm_chi2)

doc_clf = Pipeline([("tfidf", TfidfVectorizer()),
                    ("ovr", ovr_svm)])

param_grid = {
  "tfidf__sublinear_tf": [True, False],
  "ovr__estimator__chi2__k": [200, 500, 1000],
  "ovr__estimator__svm_C": [1, 10, 100]}

clf = GridSearchCV(doc_clf, param_grid, cv=10)
\end{pythoncode}
\caption{Parameter search with nested pipelines for text classification.}
\label{nested-gridsearch}
\end{figure}
